Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis.tex
analysis cut down a bit more

We investigate to what extent names in VisualGenome (\vg) and ManyNames can be considered canonical in terms of various agreement measures,
%based on annotations in \vg and ManyNames, 
and we look at sources of variation based on WordNet. %, i.e., to what extent speakers agree in their naming choices.
%Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.

@@

%As type counts give a rather rough indication for variation in object naming, 
Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
{\small
\begin{itemize}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses.% \cs{@Sina: right?}
\item \textbf{N}: the average number of types in the response set of ManyNames
\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name 
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
\end{itemize}
}
%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.

@@

If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
%In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
%For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
Across domains, however, we find a large standard deviation for both \%top and $H$.
% when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}. This indicates that the agreement varies a lot across instances\cs{", which shows that there is a high variance in agreement"(?)}, over and above the class or domain\cs{??}.
The qualitative examples in Figure \ref{fig:ex-high-low-agreement} %further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
illustrate this, showing visual instances with very high or low agreement. 
These examples suggest that instances which are more prototypical of a category trigger higher agreement.
The following section will examine other potential sources of variation in object naming.

\subsection{Variation: Specificity and Other Sources}
\label{ssec:variation}
Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
%This section shows that naming variation in ManyNames cannot be explained by this parameter.
This parameter does not explain the variation in ManyNames, as we will show in the following. 
Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
% given by \vg.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
Table \ref{tab:rel} shows the distribution
how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."} 
%\gbt{what do you mean, `` aggregated class-level response set''?}
%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
 but to other sources.

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 \\
\midrule
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
\label{tab:rel}
\end{table}

We discuss other types of variation we found in the data, based on qualitative analysis, and illustrate them with the examples in Figure\ \ref{fig:ex-high-low-agreement}:

\begin{description}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box. They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}). Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
\item[Cross-classification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
\item[Metonymy:] similar to cross-classification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loosely related synonyms or hypernyms (\textit{robe-dress}).
\end{description}

As it is non-trivial to separate this cases, we leave a precise quantitative analysis of these phenomena for future work.

>>>>

We investigate to what extent names in our dataset can be considered canonical in terms of various agreement measures,
%based on annotations in \vg and ManyNames, 
and we look at sources of variation based on WordNet. %, i.e., to what extent speakers agree in their naming choices.
%Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.

@@

%As type counts give a rather rough indication for variation in object naming, 
Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
{\small
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses.% \cs{@Sina: right?}
\item \textbf{N}: the average number of types in the response set of ManyNames
\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name 
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
\end{itemize}
}
%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.

@@

If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
%In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
%For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
Across domains, however, we find a large standard deviation for both \%top and $H$.
% when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}. This indicates that the agreement varies a lot across instances\cs{", which shows that there is a high variance in agreement"(?)}, over and above the class or domain\cs{??}.
The qualitative examples in Figure \ref{fig:ex-high-low-agreement} %further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
illustrate this, showing visual instances with very high or low agreement. 
These suggest that instances which are more prototypical of a category trigger higher agreement.
The following section will examine other potential sources of variation in object naming.

\subsection{Variation: Specificity and Other Sources}
\label{ssec:variation}
Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
%This section shows that naming variation in ManyNames cannot be explained by this parameter.
This parameter does not explain the variation in ManyNames, as we will show in the following. 
Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
% given by \vg.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
Table \ref{tab:rel} shows the distribution
how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."} 
%\gbt{what do you mean, `` aggregated class-level response set''?}
%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
 but to other sources. The following qualitative analysis discusses other types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}:

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 \\
\midrule
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

\begin{description}[style=unboxed,leftmargin=0.2cm]
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
%\setlength{\leftmargin}{0pt}
\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box. They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}). Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
\item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
\item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
\end{description}

As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
